---
title: "R Notebook"
output: html_notebook
---

when we say the running time T(n) of some program is $O(n^2)$, read "big oh of n squared" or just "oh of n squared," we mean that there are positive constants c and n0 such that for n equal to or greater than n0, we have T(n) ≤ $cn^2$. The value of n0 shown is the minimum possible value; any greater value would also work. 



Another reason for at least considering programs whose growth rates are as low as possible is that the growth rate ultimately determines how big a problem we can solve on a computer. Put another way, as computers get faster, our desire to solve larger problems on them continues to increase. 

Suppose we can afford 1000 seconds, or about 17 minutes, to solve a given problem. How large a problem can we solve? 


```{r}
x<-data.frame(value=seq(0,200))
ggplot(x)+
  geom_line(aes(x=value,y=2^x),color='red')+
  geom_line(aes(x=value,y=(x^3)/2),color='blue')+
 # geom_line(aes(x=value,y=5*x^2),color='green')+
  # geom_line(aes(x=value,y=100*x),color='black')+
  geom_vline(aes(xintercept=7))+
  ylab("t(n)")+xlab("n")+ylim(0,3000)+xlim(0,15)+
  theme_minimal()
```
Suppose that we now buy a machine that runs ten times faster at no additional cost. Then for the same cost we can spend $10^4$ seconds on a problem where we spent $10^3$ seconds before. 

```{r}
x<-data.frame(value=seq(0,200))
ggplot(x)+
  geom_line(aes(x=value,y=2^x),color='red')+
  geom_line(aes(x=value,y=(x^3)/2),color='blue')+
  geom_line(aes(x=value,y=5*x^2),color='green')+
   geom_line(aes(x=value,y=100*x),color='black')+
  geom_hline(aes(yintercept=10000))+
  ylab("t(n)")+xlab("n")+ylim(0,10000)+xlim(0,100)+
  theme_minimal()
```


```{python bubble}
def bubbleSort(alist):
    for passnum in range(len(alist)-1,0,-1):
        for i in range(passnum):
            if alist[i]>alist[i+1]:
                temp = alist[i]
                alist[i] = alist[i+1]
                alist[i+1] = temp

alist = [54,26,93,17,77,31,44,55,20]
bubbleSort(alist)
print alist
```

```{python}
import time
def sumOfN(n):
   theSum = 0
   start = time.time()

   for i in range(1,n+1):
       theSum = theSum + i
   end = time.time()   
   return theSum
   
def sumOfN2(n):
 start = time.time()
 res=(n*(n+1))/2
 end = time.time() 
 return(end-start)

   
for n in range(0,8):
    print(n,sumOfN2(10**n))
```
```{r}
library(readr)
library(ggplot2)
exp_complex<-read_delim(file="data/exp_complexity.csv",delim=" ",col_names = FALSE)

names(exp_complex)<-c('N','sumOfN','sumOfN2')
gridExtra::grid.table(exp_complex)

ggplot(exp_complex[1:7,])+
  geom_line(aes(x=N,y=sumOfN*1000),color='red',size=1)+
  geom_point(aes(x=N,y=sumOfN*1000),color='red')+
  geom_line(aes(x=N,y=sumOfN2*1000),color='blue',,size=1)+
  geom_point(aes(x=N,y=sumOfN2*1000),color='blue')+
  xlab("Tamaño[n]")+ylab("Tiempo [ms]")+
  theme_classic()+
  scale_x_continuous(labels = 10**exp_complex[1:7,]$N,breaks=exp_complex[1:7,]$N)

```



